---
title: "MANTIS: A report for Adira"
author: "Mohammad Nozari"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
runtime: shiny
---

## Summary
This report is written to help Adira's staff verify the collected data which will be used by MANTIS project. In this section, a summary of the log file is introduced.

```{r, echo=FALSE, warning=FALSE, message=FALSE}
library(shiny)
library(knitr)
library(devtools)
library(DT)
library(caret)
options(DT.options = list(pageLength = 20))

histPercent <- function(x, ...) {
   H <- hist(x, plot = FALSE)
   H$density <- with(H, 100 * density* diff(breaks)[1])
   labs <- paste(round(H$density), "%", sep="")
   plot(H, freq = FALSE, labels = labs, ylim=c(0, 1.08*max(H$density)),...)
}

# ESA.col.names <- c("ax0.ra4","ax1.ra4","ax2.ra4","ax3.ra4","ax4.ra4","ax6.ra4","ax7.ra4","LazerSafe.PCSSConditionCode","ax0.ra5","ax1.ra5","ax2.ra5","ax3.ra5","ax4.ra5","ax6.ra5","ax7.ra5","C60.0","C60.1","M5.4","M5.5","np","IO1.15","M2.9","M2.10","IO2.14","LazerSafe.CncOperationalModb.6","C70.21","C70.16","C70.17","C70.18","C70.19","C62.14","LazerSafe.PCSSReplay.2","pargene.dwgn12","IO100","IO52","IO53")
# Adira.col.names <- c("Position.Y1","Position.Y2","Position.X1","Position.X2","Position.R","Position.Z1","Position.Z2","Lazersafe.Error","Speed.Y1","Speed.Y2","Speed.X1","Speed.X2","Speed.R1","Speed.Z1","Speed.Z2","Pedal.Down","Pedal.Up","Start.NC","Stop.NC","N.Quinagem","Seq.Quinagem","Ciclo.Automatico","Ciclo.de.Quinagem","DNC.Manual","Programacao.NC","Axis.in.Position","PMS","PCV","PCL","PMI","MUTE","Comunicacao.LZS.CNC","Horas.de.trabalho","Pressure.DNC","Pressure.Machine.Y1","Pressure.Machine.Y2")
# 
# col.names <- c("time", "ax0ra4", "ax1ra4", "ax2ra4", "ax3ra4", "ax4ra4", "ax6ra4", "ax7ra4", 
#                "C6221", "ax0ra5", "ax1ra5", "ax2ra5", "ax3ra5", "ax4ra5", "ax6ra5", "ax7ra5", 
#                "C600", "C601", "M54", "M55", "np", "IO115", "M29",
#                "M210", "IO214", "lazer6", "C7021", "C7016",
#                "C7017", "C7018", "C7019", "C6214", "lazer2", "dwgn12",
#                "last1", "last2", "last3", "last4", "last5", "last6",
#                "last7")

# col.names <- Adira.col.names
outputDir <- "awesome_app"

file.name <- paste0(outputDir, "/output.csv")
dt <- read.csv(file.name, header = TRUE, sep = ",")
col.names <- colnames(dt)
```

The number of records after cleaning the data and remove the duplicates is `r nrow(dt)` and the dataset has `r ncol(dt)` columns.

```{r,echo=FALSE, warning=FALSE, message=FALSE}
col.class <- lapply(dt, class)
stat.cols <- data.frame(colname=character(),isconstant=character(),nearzero=character(),min=numeric(), mean=numeric(), max=numeric(), uniq.v=numeric())
dt$datetime <- as.character(dt$datetime)
levels(stat.cols$colname) <- colnames(dt)
levels(stat.cols$isconstant) <- c("Yes","No")
levels(stat.cols$nearzero) <- c("Yes","No")
nearzero.cols <- nearZeroVar(dt, saveMetrics = FALSE, names = TRUE)
zero.cols <- c()
row.no <- 1

for(i in 1:ncol(dt)){
  if(class(dt[,i])=="numeric" || class(dt[,i])=="integer"){
    stat.cols[row.no, c("colname")] <- colnames(dt)[i]
    stat.cols[row.no, c("min")] <- min(dt[,i], na.rm = TRUE)
    stat.cols[row.no, c("max")] <- max(dt[,i], na.rm = TRUE)
    stat.cols[row.no, c("mean")] <- mean(dt[,i], na.rm = TRUE)
    stat.cols[row.no, c("uniq.v")] <- length(unique(dt[,i]))
    if(stat.cols[row.no, c("min")]==stat.cols[row.no, c("max")])
    {
      zero.cols <- c(zero.cols, colnames(dt)[i])
      stat.cols[row.no, c("isconstant")] <- "Yes"
    }else{
      stat.cols[row.no, c("isconstant")] <- "No"
    }
    if(col.names[i] %in% nearzero.cols){
      zero.cols <- c(zero.cols, colnames(dt)[i])
      stat.cols[row.no, c("nearzero")] <- "Yes"
    }else{
      stat.cols[row.no, c("nearzero")] <- "No"
    }
    row.no <- row.no + 1
  }
}
colnames(stat.cols) <- c("Column Name","Constant","NearZero","Minimum","Average","Maximum", "Unique Values")

#library(xtable)
#print(xtable(stat.cols), type = "html")
cat("Dataset with useless columns in orange color.")
cat("\n")
DT::datatable(stat.cols, filter = 'top', callback = DT::JS("return table;"))%>% formatStyle(
  'NearZero',
  target = 'row',
  backgroundColor = styleEqual(c("Yes", "No"), c('orange', 'lightgreen'))
)%>% formatStyle(
  'Constant',
  target = 'row',
  backgroundColor = styleEqual(c("Yes", "No"), c('orange', 'lightgreen'))
)

#source: http://topepo.github.io/caret/preprocess.html
#remove constant and near zero columns
ind.remove <- which(stat.cols$`Column Name` %in% zero.cols)
stat.cols2 <- stat.cols[-ind.remove,-c(2,3)]

```

## Useful columns
Here are the basic statistics for the non-constant, non-nearzero, and without combination columns.

```{r,echo=FALSE, warning=FALSE, message=FALSE}
#source: http://shiny.rstudio.com/gallery/datatables-options.html
shinyApp(
  
  ui = fluidPage(
    DT::dataTableOutput("usefuldata")
  ),
  
  server = function(input, output) {
    output$usefuldata <- DT::renderDataTable({
      DT::datatable(stat.cols2, filter = 'top', options = list(pageLength = 25), callback = DT::JS("return table;"))%>% formatStyle(
        'Column Name',
        target = 'row',
        backgroundColor = 'lightgreen'
      )
    })
  }
)
```


```{r,echo=FALSE, warning=FALSE, message=FALSE}
char.cols <- c("time", "date", "datetime", "noDup", "timeDiff")
ind.our.col <- which(colnames(dt) %in% char.cols)
ind.col.remove <- which(colnames(dt) %in% zero.cols)
dt.noconstant <- dt[,-c(ind.our.col,ind.col.remove)]

#remove correlated columns
#ind.col.cor <- findCorrelation(cor(dt.noconstant), cutoff = .90, verbose = FALSE)
#colnames(dt.noconstant)[ind.col.cor]
#ind.col.remove <- which(colnames(dt) %in% zero.cols)


#remove linear combinations
comboInfo <- findLinearCombos(dt.noconstant)
if(!is.null(comboInfo$remove)) {dt.noconstant <- dt.noconstant[, -comboInfo$remove]}

#write clean data to the folder
dt.noconstant$time <- dt$time
dt.noconstant$date <- dt$date
dt.noconstant$datetime <- dt$datetime
dt.noconstant$noDup <- dt$noDup
dt.noconstant$timeDiff <- dt$timeDiff

write.csv(dt.noconstant,file = paste0(outputDir,"/clean-data.csv"), row.names = FALSE)

#print("Option 2")

#kable(stat.cols, digits = 2, align = c("c", rep("l", 3)), format = "markdown")
```

In the above table, you can see a basic statistics which are calculated for each column including: minimum, maximum, and average. You also have the ability to filter columns or search for specific columns or values.

## Download the clean dataset

Before analyzing each column, you can download the clean data.

```{r, echo = FALSE}
shinyApp(
  
  ui = fluidPage(
    downloadButton('downloadData', 'Download')
  ),
  
  server = function(input, output) {
    
    output$downloadData <- downloadHandler(
    
    filename = function() {
      paste0(outputDir, "/clean-data.csv")
    },
    content = function(file) {
      write.table(dt.noconstant, file, sep = ",", row.names = FALSE)
    }
  )
  }
)
```


## Explore each column
Now each column is explored to see which column has errors or inconsistent value.


```{r,echo=FALSE, warning=FALSE, message=FALSE}
dt.backup <- dt
dt <- dt.noconstant

col.names.back <- col.names
col.names <- colnames(dt)

for(j in 1:ncol(dt)){
  if(class(dt[,j])=="numeric" || class(dt[,j])=="integer"){
    cat("\n")
    cat("Column", col.names[j], "\n")
    cat("\n")
    #h <- hist(dt[,j], main = paste0("Column ", col.names[j]), labels = TRUE, xlab = paste0(col.names[j]))
    #hist(dt[,j], main = paste0("Column ", col.names[j]), labels = TRUE, xlab = paste0(col.names[j]), ylim = c(min(table(dt[,j])), sum(table(dt[,j]))))
    
    # prob=TRUE for probabilities not counts
    ##histPercent(dt[,j], col="gray", xlab = paste0(col.names[j]), main= paste0(col.names[j]))
    h <- hist(dt[,j], plot = FALSE)
    data.labels <- paste0(round(with(h, 100 * density* diff(breaks)[1]),0),"%")
    hist(dt[,j], prob=TRUE, col="lightgreen", xlab = "Column's Values",ylim = c(min(h$density),max(h$density)*1.5),main = paste0(col.names[j]))
    text(h$mids, h$density, data.labels, adj = c(.5, -.5), col = "green4", font=2)

    lines(density(dt[,j]), col="blue", lwd=2) # add a density estimate with defaults
    #lines(density(dt[,j], adjust=2), lty="dotted", col="darkgreen", lwd=2) 
  }else{
    cat("\n")
    cat("Column", col.names[j], "\n")
    cat("\n")
    cat("The number of unique values in this column is: ", length(unique(dt[,j])), "\n")
    #table(dt[,j])
  }
}
```
